Rutgers Autonomous Aircraft Team\\Technical Report\\2010 AUVSI UAS Competition

### 2010-05-22 paper/paper.tex
cogan's additions on image station

\documentclass[10pt]{report}
\usepackage[pdftex]{graphicx}
\usepackage{hyperref}
\hypersetup{ colorlinks=true
           , linkcolor=cyan
           , pdfnewwindow=true 
           }
\usepackage{amsmath}
\usepackage{subfig}
\usepackage{listings}
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\hyphenation{auto-nomous}

@@

\section{Imaging System}
COGAN, MICHAEL write an overview

@@

\subsection{Image Processing}
MICHAEL, describe flow of control and images in the camera software.

COGAN, describe computer vision algorithms, and anything else we do

\subsection{Ground Station Interface}

COGAN, describe the ground station interface

Figure goes here: COGAN, provide a screen shot of the ground station in 'action.' We should try to use images that at least look like they were taken of targets from above. Maybe take pictures from 7th floor CORE, like we said we were going to use to train the cv algorithms.

>>>>

\documentclass[10pt]{report}
\usepackage[pdftex]{graphicx}
\usepackage{hyperref}
\hypersetup{ colorlinks=true
           , linkcolor=cyan
           , pdfnewwindow=true 
           }
\usepackage{amsmath}
\usepackage{subfig}
\usepackage{listings}
\usepackage{float}
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\hyphenation{auto-nomous}

@@

\section{Imaging System}

To obtain images of targets in flight we have created an Imaging System capable of meeting all the requirements of the competition.  The system consists of a pan-tilt camera on the plane, communication software on the plane, and our ``Image Station'' application running on a dedicated laptop.  The Image Station communicates with the plane in real time via two different sets of wireless radios.  Using the Image Station, the operator can view a live video stream from the plane, control the pan-tilt camera remotely, and download and manipulate images.

@@

\subsection{Obtaining Images}

The entire imaging system is controlled by the ``Image Station Operator''.  They view a live video stream coming from the camera on the plane, which is transmitted over a high bandwidth radio.  The operator can also control the camera by sending commands to the plane over an Xbee Radio link.  In order to assist the operator in finding targets, a target locating algorithm will be run on the video feed to highlight possible targets.  At the time of writing work is in progress on this feature, and it is being implemented using the OpenCV library \cite{opencv} with contour detection and polygonal mapping functions.

\begin{figure} [H]
  \centering
  	\includegraphics[width=0.9\textwidth]{../images/ImageStationControls.jpg}
  	\caption[Image Station Control Panel]{The Control Panel for the Image Station.  Above is a live video feed from the plane.  Below are controls to adjust the pan/tilt of the unit, zoom in/out, take a picture, and reset the camera to a neutral position.}
  	\label{imagestationcontrols}
\end{figure}

When a picture is taken on the plane it is immediately saved on the camera's memory card.  In order to view that picture on the ground it must first be transferred to the plane's main computer (beagle board), and then downloaded to the Image Station over the Xbee connection.

\subsection{Downloading Images in Real Time}

Once images are on the plane's computer they are ready to be downloaded over the Xbee Radio link.  Each image is fairly large, and our bandwidth is only around 115200 baud, so we use a bandwidth conserving method to transfer images.  The entire image is first downloaded as a low-res `thumbnail.'  Once that is available for viewing, the operator can select an area of interest and download a high-res crop of just that area.  This allows us to quickly obtain high resolution images of the targets of interest.

\begin{figure} [h]
  \centering
  	\includegraphics[width=0.9\textwidth]{../images/ImageStationMain.jpg}
  	\caption[Image Station Interface]{The main interface for the Image Station.  All the images that have been taken are displayed on the top left.  The queue of images to download is on the bottom left.  On the right is the currently displayed image, with target information underneath.}
  	\label{imagestationinterface}
\end{figure}

\subsection{Identifying target characteristics}

When an image has been fully downloaded to the ground targets can be identified and tagged with metadata.  Information about the plane's orientation, gps coordinates, altitude, yaw/pitch/roll, and pan/tilt of the camera are sent down with the image.  Using this information the GPS location of the target can be determined using the intrinsic properties of the camera and some basic trigonometry. target shape, color, alphanumeric, alphanumeric color, and orienttion are all entered manually by the operator.
